Cartogram Mapping and its Application to Cancer Data Visualisation

### 2019-07-01 review_article.Rmd
html needed pandoc update

---
title: "Cartogram Mapping and its Application to Cancer Data Visualisation"
author: "Stephanie Kobakian, Jessie Roberts and Dianne Cook"
bibliography: reviewbib.bib
output:
  html_document: default
  pdf_document: default
fontsize: 11pt
link-citations: yes
number_sections: no
fig_caption: yes
biblio-style: vancouver
---

>>>>

---
title: "Cartogram Mapping and its Application to Cancer Data Visualisation"
author: "Stephanie Kobakian, Jessie Roberts and Dianne Cook"
bibliography: reviewbib.bib
output:
  html_document: default
fontsize: 11pt
link-citations: yes
number_sections: no
fig_caption: yes
biblio-style: vancouver
---
